\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

% Font Options
\usepackage[sfdefault]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\addtolength{\footskip}{0.2in}    % Adds space at the bottom equivalent to the top margin


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Resume Starts Here

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Sudhanshu Jha} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:9870470738}{+91 9870470738}
    $|$
    \faAt \hspace{.5pt} \href{mailto:jha.sudhanshu28@gmail.com}{jha.sudhanshu28@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/sudhanshu-jha28/}{sudhanshu-jha}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Sud-7}{Sud-7}
    $|$
    \faMapMarker \hspace{.5pt} Noida, U.P., India
\end{center}

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
    \resumeSubheading
      {UST Global}{Noida, India}
      {Associate - I, Cloud Infrastructure Services}{Apr 2023 -- Apr 2024}
        \resumeItemListStart
            \resumeItem{Developed and implemented a sophisticated chatbot application, serving as a pivotal tool for client organizations to efficiently address technical issues among their employees.}
            \resumeItem{Collaborated with a team of developers and product managers to design, develop, and maintain the chatbot.}
            \resumeItem{Implemented reusable React components and libraries, enhancing code modularity and improving development efficiency.}
            \resumeItem{Ensured accurate implementation of UI/UX designs and maintained a consistent visual aesthetic by closely collaborating with the design team.}
            \resumeItem{Integrated RESTful APIs for backend communication and worked with QA to develop and execute test plans, ensuring application stability and reliability.}
           
        \resumeItemListEnd
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------
\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart


    \resumeProjectHeading
      {\textbf{Food Delivery App (Zomato Clone)} \textbf{- (NextJS, MongoDB, Redux-toolkit) }}{2024}
        \resumeItemListStart
            \resumeItem{Developed a full-featured food delivery app, allowing users to register, authenticate, and manage their restaurants, including adding food items to their respective pages, with data stored in MongoDB.}
            \resumeItem{Implemented secure login and authentication mechanisms, ensuring user data integrity and controlled access to restaurant management features.
}
            \resumeItem{Designed an intuitive landing page with a robust search functionality, improving user engagement and ease of navigation.}
\resumeItem{Utilized NextJS for building a responsive and scalable application, optimized for seamless performance across devices.}
            \resumeItem{Deployed: \href{https://zomato-clone-next-js.vercel.app}{zomato-clone-next-js.vercel.app}} 
            \resumeItem{{CodeBase: \href{https://github.com/Sud-7/Zomato-clone-NextJS}{github.com/Sud-7/Zomato-clone-NextJS}}}
        \resumeItemListEnd

    
    \resumeProjectHeading
      {\textbf{User Add Todo}  \textbf {- (NextJS, Redux-Toolkit with Local Storage Persistence, MongoDB) }} {2024}
        \resumeItemListStart
            \resumeItem{Developed a dynamic Todo application using NextJS, implementing full CRUD operations connected to MongoDB for robust backend data management.}
            \resumeItem{Employed Redux Toolkit for state management, ensuring efficient and scalable handling of application state.}
            \resumeItem{Integrated Local Storage for persistent state across sessions, enhancing user experience by retaining data locally.}
\resumeItem{Maintained a clean and modular codebase, utilizing Git for version control to support continuous development and collaboration.}
            \resumeItem{Deployed: \href{https://next-redux-basic.vercel.app/}{next-redux-basic.vercel.app/}}
            \resumeItem{CodeBase: \href{https://github.com/Sud-7/Next-redux-basic}{github.com/Sud-7/Next-redux-basic}}
        \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Counter App}  \textbf {- (ReactJS, Redux-Toolkit with Local Storage Persistence) }}{2024}
        \resumeItemListStart
            \resumeItem{Developed a responsive web application with ReactJS, leveraging Redux Toolkit for efficient state management.}
            \resumeItem{Integrated data persistence using Local Storage to ensure state retention across user sessions.}
            \resumeItem{Implemented robust functionalities for managing application state, including adding, updating, and deleting data entries.}
            \resumeItem{Deployed: \href{https://redux-counter-app-beta.vercel.app/}{redux-counter-app-beta.vercel.app/}}
            \resumeItem{CodeBase: \href{https://github.com/Sud-7/redux-counter-app}{github.com/Sud-7/redux-counter-app}}
        \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Capticon - Add captions to videos} \textbf{- (ReactJS,TailwindCSS)}}{2024}
        \resumeItemListStart
            \resumeItem{Built a dynamic web application that allows users to input captions with timestamps and synchronize them with video playback.}
            \resumeItem{Implemented key functionalities for adding, validating, and removing caption entries with Timestamp using React.}
            \resumeItem{Integrated video playback functionality with synchronized caption display.}
            \resumeItem{Used Git for version control, maintaining a well-documented codebase and facilitating collaborative development.}
           
            \resumeItem{Deployed: \href{https://capticoninator.web.app/}{capticoninator.web.app}}
            \resumeItem{CodeBase: \href{https://github.com/Sud-7/Capticon}{github.com/Sud-7/Capticon}}
        \resumeItemListEnd


%----------- EDUCATION -----------
\section{Education}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {Amity Institute of Technology}{Noida, India}
      {B.Tech.; \textbf{GPA: 7.3/10}}{Jul 2017 -- Jun 2021}
    \resumeEducationHeading
      {Vanasthali Public School}{Noida, India}
      {High School; \textbf{Percentage: 73\%}}{Apr 2016 -- Mar 2017}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------
\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \item{
        \textbf{Frameworks:}{ NextJS, Redux-toolkit(library), ReactJS, NodeJS, Bootstrap, ExpressJS, TailwindCSS, react-router} \\
        \textbf{Programming:}{ TypeScript, JavaScript, Python, HTML5, CSS3} \\
        \textbf{Database:}{ MongoDB, PostgresSQL} \\
        \textbf{Tools:}{ Babel, Firebase, NPM, pip,  VScode, GitHub, Vercel} \\
    }
  \resumeSubHeadingListEnd

\end{document}
